Replicating the \"Money Illusion\" Effect: Exploring Gender Influences within a Brazilian Sample

### 2024-02-13 outputs/paper/paper.qmd
added data cleaning steps

---
title: "Student Replication for \"Money Illusion\""
title-block-banner: true
abstract: "Money illusion as the tendency to overlook the impact of inflation which  focusing on nominal values identified by Shafir, Diamond, and Tversky (1997). This study reproduce four scenarios from research where participants face financial decisions influenced by money illusion in various situations such as earnings, transactions, and contracts,under the background of Brazilian context, where in various situations such as transactions, transactions and earnings that participants face financial decisions influenced by money illusion. The cross-sectional and pre-registered research is based on 372 Brazilian participants in mobile phones or computers by using chi-square tests assessed money illusion. The results indicate that participants' tend to choose financially advantages opportunities which  influenced by the framing of terms (real, nominal, or neutral). After we replicate across all four scenarios, the findings suggest that the money illusion effect  transcend cultural boundaries, supported by replication within a different background of cultural context."
thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Student-Replication-For-Money-Illusion.git"
author: "Terry Tu, Jingyi Shen, Yaning Jin "
date: today
date-format: long
format: pdf
toc: true
toc-depth: 2
number-sections: true
bibliography: references.bib
link-citations: true
---

@@

@@

@@

>>>>

---
title: "Replicating the \"Money Illusion\" Effect: Exploring Gender Influences within a Brazilian Sample"
title-block-banner: true
abstract: "Money illusion as the tendency to overlook the impact of inflation which  focusing on nominal values identified by Shafir, Diamond, and Tversky (1997). This study reproduce four scenarios from research where participants face financial decisions influenced by money illusion in various situations such as earnings, transactions, and contracts,under the background of Brazilian context, where in various situations such as transactions, transactions and earnings that participants face financial decisions influenced by money illusion. The cross-sectional and pre-registered research is based on 372 Brazilian participants in mobile phones or computers by using chi-square tests assessed money illusion. The results indicate that participants' tend to choose financially advantages opportunities which  influenced by the framing of terms (real, nominal, or neutral). After we replicate across all four scenarios, the findings suggest that the money illusion effect  transcend cultural boundaries, supported by replication within a different background of cultural context."
thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Student-Replication-For-Money-Illusion.git"
author: "Terry Tu, Jingyi Shen, Yaning Jin "
date: today
date-format: long
format: pdf
toc: true
toc-depth: 2
number-sections: true
bibliography: references.bib
link-citations: true
---

```{r setup, include=FALSE, message=FALSE}
# Un-comment these lines for missing packages
# install.packages("lubridate")
# install.packages("dplyr")
# install.packages("ggplot2")
# install.packages("here")
# install.packages("readr")
# install.packages("tidyverse")
# install.packages("readxl")

## Import nessasay libraries
library(readxl)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(here)
library(readr)
knitr::opts_chunk$set(echo = FALSE)
```

@@

```{r include=FALSE, message=FALSE}
# read the data file and store it in the 'data' variable
data <- readxl::read_excel(here("inputs", "data", "money_data_raw.xlsx"))
```

@@

### Data Cleaning

### Data Sample

```{r table1, echo=FALSE}
knitr::kable(head(data, 6), 
             caption = "Sample of the Cleaned TTC Subway Delay Data",
             format = "markdown")
```

### Measurement

@@

### Problem 1: 
```{r fig-problem1, echo=FALSE, fig.cap=""}

```
